\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath}
\title{rcrk24}
\author{Alex Kim}
\date{July 2024}

\begin{document}

 \maketitle

\section{Model Description}
The distinguishing features of the {\tt rcrk24} model are
\begin{itemize}
\item Includes redshift dependence.
\item Uses the first-order approximation for the evolution of growth
\begin{equation}
{P_{xy}} = {\sigma^2_8} \frac{P^{(f)}_{xy}}{\sigma^{2(f)}_8},
\end{equation}
where the ${}^{(f)}$ superscript refers to the input fiducial model.
\item
The background expansion history, specifically $H(a)$ is assumed to be known and so is not dependent
on any model parameters.
\end{itemize}

For observables $\alpha$, $\beta$ at $z_1$, $z_2$
\begin{equation}
P_{\alpha\beta}(z_1,z_2)= A_\alpha(z_1) A_\beta(z_2) \frac{P^{(f)}_{xy}}{\sigma^{2(f)}_8}.
\end{equation}
$A_\alpha$ are the product of several terms.
These terms and their partial derivatives are implemented in {\tt coefficients}.
\footnote{Though logically the partial derivatives would be implemented in
{\tt fisher\_terms}, it is easier to maintain consistency by keeping everything in the same file.}
$A_\alpha$ is calculated in {\tt coefficients.get\_coefficients} and the partials
of $A_\alpha$ are calculated in {\tt fisher\_terms.get\_partial\_derivative\_coefficients}.

\begin{itemize}
\item $A_v(z) = a(z)H(z)f(z)\sigma_8(z)$.
\item $A_\delta(z)$ not yet implemented.
\end{itemize}
\section{Variants}

There are two variants:
\begin{description}
\item[growth\_rate] $f\sigma_8=\text{constant}$.
\item[growth\_index] $f=\Omega_{M}^\gamma$, $\sigma_8  = \sigma_{8,\text{cmb}}  e^{\int^{\ln{a}}_{\ln{a_\text{CMB}}} \Omega_M^\gamma d\ln{a'}} $ with free parameters $\Omega_{M0}$ and $\gamma$.
\end{description}

\subsection{growth\_rate}

The parameter that describes the model is
{\tt fs8}: $f\sigma_8$.

\subsubsection{$A_v$}
\begin{align}
A_{v}(z) & = a(z) H(z) f\sigma_8 \\
\frac{\partial A_{v}}{\partial f\sigma_8} (z) & = a(z) H(z)
\end{align}

\subsection{growth\_index}
The following functions are associated with the model
\begin{align}
\sigma_8(a) & = \sigma_{8,\text{cmb}}  e^{\int^{\ln{a}}_{\ln{a_\text{CMB}}} \Omega_M^\gamma d\ln{a'}} \\
\Omega_M & = \frac{\Omega_{M0} a^{-3}}{\Omega_{M0} a^{-3} + 1 - \Omega_{M0}}\\
\frac{d\Omega_M}{d\Omega_{M0}} & = \frac{a^{-3}}{\Omega_{M0} a^{-3} + 1 - \Omega_{M0}} - \frac{\Omega_{M0} a^{-3}(a^{-3}-1)}{(\Omega_{M0} a^{-3} + 1 - \Omega_{M0})^2}.
\end{align}
The value of $ \sigma_{8,\text{cmb}}= 0.832 * 0.001176774706956903$ based on the PDG and the scale factor
of at $z=1089.92$ for $\Omega_{M0}=0.3$ and $\gamma=0.5$.

The parameters that describe the model are {\tt gamma}:$\gamma$; {\tt Om0}:$\Omega_{M0}$

\subsubsection{$A_v$}

\begin{align}
A_{v}(z) & =a(z) H(z) \Omega_M^\gamma  \sigma_8(a) \\
\frac{\partial A_{v}}{\partial \gamma} (z) & = a(z) H(z)
\left( \ln{\Omega_M}   + 
 e^{\int^{\ln{a}}_{\ln{a_\text{CMB}}}\left( \ln{\Omega_M} \right) \Omega_M^\gamma d\ln{a}}
\right) \Omega_M^\gamma  \sigma_8(a) \\
\frac{\partial A_{v}}{\partial \Omega_M0} (z) & =a(z)  H(z) 
\left( \gamma  \frac{d\Omega_M}{d\Omega_{M0}} \Omega_M^{-1}  + 
 e^{\int^{\ln{a}}_{\ln{a_\text{CMB}}}\gamma \frac{d\Omega_M}{d\Omega_{M0}} \Omega^{\gamma-1} d\ln{a'}}
\right) \Omega^\gamma  \sigma_8(a).
\end{align}

For numerical efficiency it is useful to use
\begin{align}
\sigma_8(a) & =\sigma_{8,\text{cmb}}  
 e^{\int^1_{\ln{a_\text{CMB}}} \Omega_M^\gamma d\ln{a} - \int_{\ln{a}}^1 \Omega_M^\gamma d\ln{a'} } 
\end{align}
and
\begin{equation}
\int_{\ln{a}}^0 \Omega_M^\gamma d\ln{a'} \approx -\ln{a} \left[\Omega_{M0}^\gamma + \Omega_{M0}^\gamma 3\gamma(1-\Omega_{M0} )\right] 
- (1-a) \Omega_{M0}^\gamma 3\gamma (1-\Omega_{M0}).
\end{equation}
to approximate $A$ and its partial derivatives (though implemented in code I am too lazy to write this in LaTeX for the moment).  This solution is the default as hardwired in {\tt fisher\_terms.exact=False}.  Making this configurable requires some work.

\end{document}
